\documentclass[14pt]{extbook}
\usepackage{multicol, enumerate, enumitem, hyperref, color, soul, setspace, parskip, fancyhdr} %General Packages
\usepackage{amssymb, amsthm, amsmath, latexsym, units, mathtools} %Math Packages
\everymath{\displaystyle} %All math in Display Style
% Packages with additional options
\usepackage[headsep=0.5cm,headheight=12pt, left=1 in,right= 1 in,top= 1 in,bottom= 1 in]{geometry}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{dashrule}  % Package to use the command below to create lines between items
\newcommand{\litem}[1]{\item#1\hspace*{-1cm}\rule{\textwidth}{0.4pt}}
\pagestyle{fancy}
\lhead{Makeup Progress Quiz 2}
\chead{}
\rhead{Version A}
\lfoot{5763-3522}
\cfoot{}
\rfoot{Spring 2021}
\begin{document}

\begin{enumerate}
\litem{
Find the inverse of the function below (if it exists). Then, evaluate the inverse at $x = -10$ and choose the interval the $f^{-1}(-10)$ belongs to.\[ f(x) = \sqrt[3]{3 x + 4} \]\begin{enumerate}[label=\Alph*.]
\item \( f^{-1}(-10) \in [-336.8, -332.9] \)
\item \( f^{-1}(-10) \in [-332.2, -330.5] \)
\item \( f^{-1}(-10) \in [330.5, 333] \)
\item \( f^{-1}(-10) \in [334.6, 336.7] \)
\item \( \text{ The function is not invertible for all Real numbers. } \)

\end{enumerate} }
\litem{
Subtract the following functions, then choose the domain of the resulting function from the list below.\[ f(x) = \frac{5}{5x-16} \text{ and } g(x) = \frac{1}{5x+32} \]\begin{enumerate}[label=\Alph*.]
\item \( \text{ The domain is all Real numbers except } x = a, \text{ where } a \in [-6.33, -0.33] \)
\item \( \text{ The domain is all Real numbers greater than or equal to } x = a, \text{ where } a \in [0.2, 4.2] \)
\item \( \text{ The domain is all Real numbers less than or equal to } x = a, \text{ where } a \in [-2.75, -0.75] \)
\item \( \text{ The domain is all Real numbers except } x = a \text{ and } x = b, \text{ where } a \in [1.2, 10.2] \text{ and } b \in [-7.4, -2.4] \)
\item \( \text{ The domain is all Real numbers. } \)

\end{enumerate} }
\litem{
Determine whether the function below is 1-1.\[ f(x) = (5 x + 26)^3 \]\begin{enumerate}[label=\Alph*.]
\item \( \text{No, because the range of the function is not $(-\infty, \infty)$.} \)
\item \( \text{No, because there is an $x$-value that goes to 2 different $y$-values.} \)
\item \( \text{No, because the domain of the function is not $(-\infty, \infty)$.} \)
\item \( \text{No, because there is a $y$-value that goes to 2 different $x$-values.} \)
\item \( \text{Yes, the function is 1-1.} \)

\end{enumerate} }
\litem{
Find the inverse of the function below. Then, evaluate the inverse at $x = 9$ and choose the interval that $f^{-1}(9)$ belongs to.\[ f(x) = \ln{(x-2)}-5 \]\begin{enumerate}[label=\Alph*.]
\item \( f^{-1}(9) \in [1202595.28, 1202603.28] \)
\item \( f^{-1}(9) \in [54.6, 61.6] \)
\item \( f^{-1}(9) \in [1202606.28, 1202608.28] \)
\item \( f^{-1}(9) \in [59867.14, 59870.14] \)
\item \( f^{-1}(9) \in [1090.63, 1092.63] \)

\end{enumerate} }
\litem{
Find the inverse of the function below. Then, evaluate the inverse at $x = 7$ and choose the interval that $f^{-1}(7)$ belongs to.\[ f(x) = e^{x+3}-5 \]\begin{enumerate}[label=\Alph*.]
\item \( f^{-1}(7) \in [-1.25, -0.49] \)
\item \( f^{-1}(7) \in [-4.92, -3.94] \)
\item \( f^{-1}(7) \in [-3.18, -2.2] \)
\item \( f^{-1}(7) \in [5.44, 5.58] \)
\item \( f^{-1}(7) \in [-4.04, -3.46] \)

\end{enumerate} }
\litem{
Determine whether the function below is 1-1.\[ f(x) = 30 x^2 - 2 x - 572 \]\begin{enumerate}[label=\Alph*.]
\item \( \text{No, because there is a $y$-value that goes to 2 different $x$-values.} \)
\item \( \text{Yes, the function is 1-1.} \)
\item \( \text{No, because there is an $x$-value that goes to 2 different $y$-values.} \)
\item \( \text{No, because the domain of the function is not $(-\infty, \infty)$.} \)
\item \( \text{No, because the range of the function is not $(-\infty, \infty)$.} \)

\end{enumerate} }
\litem{
Multiply the following functions, then choose the domain of the resulting function from the list below.\[ f(x) = 8x^{3} +3 x^{2} +4 x + 6 \text{ and } g(x) = 2x \]\begin{enumerate}[label=\Alph*.]
\item \( \text{ The domain is all Real numbers less than or equal to } x = a, \text{ where } a \in [-4, 1] \)
\item \( \text{ The domain is all Real numbers except } x = a, \text{ where } a \in [-7.83, -2.83] \)
\item \( \text{ The domain is all Real numbers greater than or equal to } x = a, \text{ where } a \in [-6, 0] \)
\item \( \text{ The domain is all Real numbers except } x = a \text{ and } x = b, \text{ where } a \in [-9.83, 1.17] \text{ and } b \in [3.4, 9.4] \)
\item \( \text{ The domain is all Real numbers. } \)

\end{enumerate} }
\litem{
Choose the interval below that $f$ composed with $g$ at $x=1$ is in.\[ f(x) = 3x^{3} -4 x^{2} +x \text{ and } g(x) = -3x^{3} +2 x^{2} +4 x -3 \]\begin{enumerate}[label=\Alph*.]
\item \( (f \circ g)(1) \in [-5.96, -4.16] \)
\item \( (f \circ g)(1) \in [-0.43, 1.14] \)
\item \( (f \circ g)(1) \in [1.83, 2.2] \)
\item \( (f \circ g)(1) \in [-4.58, -1.54] \)
\item \( \text{It is not possible to compose the two functions.} \)

\end{enumerate} }
\litem{
Choose the interval below that $f$ composed with $g$ at $x=-1$ is in.\[ f(x) = -x^{3} -4 x^{2} +2 x + 3 \text{ and } g(x) = 4x^{3} -2 x^{2} -x \]\begin{enumerate}[label=\Alph*.]
\item \( (f \circ g)(-1) \in [14, 24] \)
\item \( (f \circ g)(-1) \in [2, 9] \)
\item \( (f \circ g)(-1) \in [-44, -36] \)
\item \( (f \circ g)(-1) \in [-49, -42] \)
\item \( \text{It is not possible to compose the two functions.} \)

\end{enumerate} }
\litem{
Find the inverse of the function below (if it exists). Then, evaluate the inverse at $x = -12$ and choose the interval that $f^{-1}(-12)$ belongs to.\[ f(x) = 2 x^2 + 3 \]\begin{enumerate}[label=\Alph*.]
\item \( f^{-1}(-12) \in [3.98, 5.38] \)
\item \( f^{-1}(-12) \in [2.45, 3.1] \)
\item \( f^{-1}(-12) \in [1.66, 2.17] \)
\item \( f^{-1}(-12) \in [3.65, 4.12] \)
\item \( \text{ The function is not invertible for all Real numbers. } \)

\end{enumerate} }
\end{enumerate}

\end{document}