\documentclass[14pt]{extbook}
\usepackage{multicol, enumerate, enumitem, hyperref, color, soul, setspace, parskip, fancyhdr} %General Packages
\usepackage{amssymb, amsthm, amsmath, latexsym, units, mathtools} %Math Packages
\everymath{\displaystyle} %All math in Display Style
% Packages with additional options
\usepackage[headsep=0.5cm,headheight=12pt, left=1 in,right= 1 in,top= 1 in,bottom= 1 in]{geometry}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{dashrule}  % Package to use the command below to create lines between items
\newcommand{\litem}[1]{\item#1\hspace*{-1cm}\rule{\textwidth}{0.4pt}}
\pagestyle{fancy}
\lhead{Makeup Progress Quiz 2}
\chead{}
\rhead{Version B}
\lfoot{5763-3522}
\cfoot{}
\rfoot{Spring 2021}
\begin{document}

\begin{enumerate}
\litem{
Find the inverse of the function below (if it exists). Then, evaluate the inverse at $x = -15$ and choose the interval that $f^{-1}(-15)$ belongs to.\[ f(x) = 4 x^2 + 5 \]\begin{enumerate}[label=\Alph*.]
\item \( f^{-1}(-15) \in [1.71, 3.74] \)
\item \( f^{-1}(-15) \in [3.46, 5.19] \)
\item \( f^{-1}(-15) \in [6.17, 7.76] \)
\item \( f^{-1}(-15) \in [0.86, 2.11] \)
\item \( \text{ The function is not invertible for all Real numbers. } \)

\end{enumerate} }
\litem{
Multiply the following functions, then choose the domain of the resulting function from the list below.\[ f(x) = 2x^{2} +5 x + 9 \text{ and } g(x) = \sqrt{-3x+6}  \]\begin{enumerate}[label=\Alph*.]
\item \( \text{ The domain is all Real numbers except } x = a, \text{ where } a \in [-6.33, -3.33] \)
\item \( \text{ The domain is all Real numbers less than or equal to } x = a, \text{ where } a \in [1, 6] \)
\item \( \text{ The domain is all Real numbers greater than or equal to } x = a, \text{ where } a \in [-8, -4] \)
\item \( \text{ The domain is all Real numbers except } x = a \text{ and } x = b, \text{ where } a \in [-7.33, -3.33] \text{ and } b \in [4.33, 7.33] \)
\item \( \text{ The domain is all Real numbers. } \)

\end{enumerate} }
\litem{
Determine whether the function below is 1-1.\[ f(x) = (5 x + 23)^3 \]\begin{enumerate}[label=\Alph*.]
\item \( \text{No, because the domain of the function is not $(-\infty, \infty)$.} \)
\item \( \text{No, because there is a $y$-value that goes to 2 different $x$-values.} \)
\item \( \text{Yes, the function is 1-1.} \)
\item \( \text{No, because the range of the function is not $(-\infty, \infty)$.} \)
\item \( \text{No, because there is an $x$-value that goes to 2 different $y$-values.} \)

\end{enumerate} }
\litem{
Find the inverse of the function below. Then, evaluate the inverse at $x = 6$ and choose the interval that $f^{-1}(6)$ belongs to.\[ f(x) = \ln{(x+4)}+4 \]\begin{enumerate}[label=\Alph*.]
\item \( f^{-1}(6) \in [22027.47, 22031.47] \)
\item \( f^{-1}(6) \in [7.39, 16.39] \)
\item \( f^{-1}(6) \in [7.39, 16.39] \)
\item \( f^{-1}(6) \in [22019.47, 22024.47] \)
\item \( f^{-1}(6) \in [-0.61, 6.39] \)

\end{enumerate} }
\litem{
Find the inverse of the function below. Then, evaluate the inverse at $x = 9$ and choose the interval that $f^{-1}(9)$ belongs to.\[ f(x) = e^{x+5}+4 \]\begin{enumerate}[label=\Alph*.]
\item \( f^{-1}(9) \in [6.61, 6.65] \)
\item \( f^{-1}(9) \in [6.57, 6.63] \)
\item \( f^{-1}(9) \in [-3.4, -3.38] \)
\item \( f^{-1}(9) \in [5.37, 5.4] \)
\item \( f^{-1}(9) \in [6.55, 6.57] \)

\end{enumerate} }
\litem{
Determine whether the function below is 1-1.\[ f(x) = 9 x^2 - 120 x + 400 \]\begin{enumerate}[label=\Alph*.]
\item \( \text{Yes, the function is 1-1.} \)
\item \( \text{No, because there is an $x$-value that goes to 2 different $y$-values.} \)
\item \( \text{No, because the domain of the function is not $(-\infty, \infty)$.} \)
\item \( \text{No, because there is a $y$-value that goes to 2 different $x$-values.} \)
\item \( \text{No, because the range of the function is not $(-\infty, \infty)$.} \)

\end{enumerate} }
\litem{
Add the following functions, then choose the domain of the resulting function from the list below.\[ f(x) = 7x \text{ and } g(x) = \sqrt{5x-32}  \]\begin{enumerate}[label=\Alph*.]
\item \( \text{ The domain is all Real numbers except } x = a, \text{ where } a \in [-7.67, -1.67] \)
\item \( \text{ The domain is all Real numbers less than or equal to } x = a, \text{ where } a \in [-7.17, -2.17] \)
\item \( \text{ The domain is all Real numbers greater than or equal to } x = a, \text{ where } a \in [3.4, 9.4] \)
\item \( \text{ The domain is all Real numbers except } x = a \text{ and } x = b, \text{ where } a \in [-5.67, -0.67] \text{ and } b \in [-14.33, -0.33] \)
\item \( \text{ The domain is all Real numbers. } \)

\end{enumerate} }
\litem{
Choose the interval below that $f$ composed with $g$ at $x=1$ is in.\[ f(x) = -2x^{3} -3 x^{2} +3 x \text{ and } g(x) = 3x^{3} +4 x^{2} -4 x \]\begin{enumerate}[label=\Alph*.]
\item \( (f \circ g)(1) \in [-2, 2] \)
\item \( (f \circ g)(1) \in [-74, -69] \)
\item \( (f \circ g)(1) \in [6, 12] \)
\item \( (f \circ g)(1) \in [-87, -74] \)
\item \( \text{It is not possible to compose the two functions.} \)

\end{enumerate} }
\litem{
Choose the interval below that $f$ composed with $g$ at $x=1$ is in.\[ f(x) = -3x^{3} +2 x^{2} -x + 1 \text{ and } g(x) = 4x^{3} +3 x^{2} -x -4 \]\begin{enumerate}[label=\Alph*.]
\item \( (f \circ g)(1) \in [-26, -19] \)
\item \( (f \circ g)(1) \in [-5, -2] \)
\item \( (f \circ g)(1) \in [2, 6] \)
\item \( (f \circ g)(1) \in [-19, -11] \)
\item \( \text{It is not possible to compose the two functions.} \)

\end{enumerate} }
\litem{
Find the inverse of the function below (if it exists). Then, evaluate the inverse at $x = -15$ and choose the interval that $f^{-1}(-15)$ belongs to.\[ f(x) = 3 x^2 - 2 \]\begin{enumerate}[label=\Alph*.]
\item \( f^{-1}(-15) \in [1.78, 2.12] \)
\item \( f^{-1}(-15) \in [5.99, 6.23] \)
\item \( f^{-1}(-15) \in [3.05, 3.15] \)
\item \( f^{-1}(-15) \in [2.25, 2.46] \)
\item \( \text{ The function is not invertible for all Real numbers. } \)

\end{enumerate} }
\end{enumerate}

\end{document}