\documentclass[14pt]{extbook}
\usepackage{multicol, enumerate, enumitem, hyperref, color, soul, setspace, parskip, fancyhdr} %General Packages
\usepackage{amssymb, amsthm, amsmath, bbm, latexsym, units, mathtools} %Math Packages
\everymath{\displaystyle} %All math in Display Style
% Packages with additional options
\usepackage[headsep=0.5cm,headheight=12pt, left=1 in,right= 1 in,top= 1 in,bottom= 1 in]{geometry}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{dashrule}  % Package to use the command below to create lines between items
\newcommand{\litem}[1]{\item#1\hspace*{-1cm}\rule{\textwidth}{0.4pt}}
\pagestyle{fancy}
\lhead{Module9L}
\chead{}
\rhead{Version B}
\lfoot{3286-3678}
\cfoot{}
\rfoot{testing}
\begin{document}

\begin{enumerate}
\litem{
Determine whether the function below is 1-1.\[ f(x) = 9 x^2 + 15 x - 456 \]\begin{enumerate}[label=\Alph*.]
\item \( \text{No, because there is a $y$-value that goes to 2 different $x$-values.} \)
\item \( \text{No, because there is an $x$-value that goes to 2 different $y$-values.} \)
\item \( \text{Yes, the function is 1-1.} \)
\item \( \text{No, because the domain of the function is not $(-\infty, \infty)$.} \)
\item \( \text{No, because the range of the function is not $(-\infty, \infty)$.} \)

\end{enumerate} }
\litem{
Choose the interval below that $f$ composed with $g$ at $x=-1$ is in.\[ f(x) = x^{3} -4 x^{2} +x \text{ and } g(x) = x^{3} +4 x^{2} -x \]\begin{enumerate}[label=\Alph*.]
\item \( (f \circ g)(-1) \in [2, 8] \)
\item \( (f \circ g)(-1) \in [-67, -61] \)
\item \( (f \circ g)(-1) \in [-3, 1] \)
\item \( (f \circ g)(-1) \in [-83, -73] \)
\item \( \text{It is not possible to compose the two functions.} \)

\end{enumerate} }
\litem{
Subtract the following functions, then choose the domain of the resulting function from the list below.\[ f(x) = x^{4} +5 x^{3} +5 x^{2} + 2 \text{ and } g(x) = \frac{5}{4x+15} \]\begin{enumerate}[label=\Alph*.]
\item \( \text{ The domain is all Real numbers except } x = a, \text{ where } a \in [-3.75, 0.25] \)
\item \( \text{ The domain is all Real numbers greater than or equal to } x = a, \text{ where } a \in [-9.25, -2.25] \)
\item \( \text{ The domain is all Real numbers less than or equal to } x = a, \text{ where } a \in [-2, 0] \)
\item \( \text{ The domain is all Real numbers except } x = a \text{ and } x = b, \text{ where } a \in [-8.33, 1.67] \text{ and } b \in [6.2, 7.2] \)
\item \( \text{ The domain is all Real numbers. } \)

\end{enumerate} }
\litem{
Find the inverse of the function below. Then, evaluate the inverse at $x = 9$ and choose the interval that $f^{-1}(9)$ belongs to.\[ f(x) = e^{x-4}-3 \]\begin{enumerate}[label=\Alph*.]
\item \( f^{-1}(9) \in [-1.36, -1.19] \)
\item \( f^{-1}(9) \in [-0.61, -0.43] \)
\item \( f^{-1}(9) \in [-1.43, -1.22] \)
\item \( f^{-1}(9) \in [-1.76, -1.5] \)
\item \( f^{-1}(9) \in [6.36, 6.51] \)

\end{enumerate} }
\litem{
Find the inverse of the function below (if it exists). Then, evaluate the inverse at $x = -11$ and choose the interval the $f^{-1}(-11)$ belongs to.\[ f(x) = \sqrt[3]{2 x - 3} \]\begin{enumerate}[label=\Alph*.]
\item \( f^{-1}(-11) \in [663.1, 665.4] \)
\item \( f^{-1}(-11) \in [-668.4, -665.4] \)
\item \( f^{-1}(-11) \in [-665.8, -660.6] \)
\item \( f^{-1}(-11) \in [666.8, 669.9] \)
\item \( \text{ The function is not invertible for all Real numbers. } \)

\end{enumerate} }
\litem{
Add the following functions, then choose the domain of the resulting function from the list below.\[ f(x) = \frac{5}{3x-16} \text{ and } g(x) = \frac{3}{4x+21} \]\begin{enumerate}[label=\Alph*.]
\item \( \text{ The domain is all Real numbers except } x = a, \text{ where } a \in [4.33, 12.33] \)
\item \( \text{ The domain is all Real numbers less than or equal to } x = a, \text{ where } a \in [-5.67, 2.33] \)
\item \( \text{ The domain is all Real numbers greater than or equal to } x = a, \text{ where } a \in [3.75, 7.75] \)
\item \( \text{ The domain is all Real numbers except } x = a \text{ and } x = b, \text{ where } a \in [4.33, 7.33] \text{ and } b \in [-9.25, -3.25] \)
\item \( \text{ The domain is all Real numbers. } \)

\end{enumerate} }
\litem{
Choose the interval below that $f$ composed with $g$ at $x=-1$ is in.\[ f(x) = -2x^{3} +2 x^{2} +4 x + 3 \text{ and } g(x) = 2x^{3} + x^{2} -4 x + 1 \]\begin{enumerate}[label=\Alph*.]
\item \( (f \circ g)(-1) \in [-79, -74] \)
\item \( (f \circ g)(-1) \in [-68, -67] \)
\item \( (f \circ g)(-1) \in [51, 55] \)
\item \( (f \circ g)(-1) \in [39, 48] \)
\item \( \text{It is not possible to compose the two functions.} \)

\end{enumerate} }
\litem{
Find the inverse of the function below (if it exists). Then, evaluate the inverse at $x = 10$ and choose the interval the $f^{-1}(10)$ belongs to.\[ f(x) = \sqrt[3]{3 x + 2} \]\begin{enumerate}[label=\Alph*.]
\item \( f^{-1}(10) \in [-334.41, -333.58] \)
\item \( f^{-1}(10) \in [332.26, 333.46] \)
\item \( f^{-1}(10) \in [333.98, 334.06] \)
\item \( f^{-1}(10) \in [-333.03, -332.01] \)
\item \( \text{ The function is not invertible for all Real numbers. } \)

\end{enumerate} }
\litem{
Find the inverse of the function below. Then, evaluate the inverse at $x = 9$ and choose the interval that $f^{-1}(9)$ belongs to.\[ f(x) = e^{x-2}+5 \]\begin{enumerate}[label=\Alph*.]
\item \( f^{-1}(9) \in [3.15, 3.4] \)
\item \( f^{-1}(9) \in [7.34, 7.43] \)
\item \( f^{-1}(9) \in [7.59, 7.66] \)
\item \( f^{-1}(9) \in [6.77, 7.03] \)
\item \( f^{-1}(9) \in [-0.78, -0.44] \)

\end{enumerate} }
\litem{
Determine whether the function below is 1-1.\[ f(x) = 36 x^2 - 348 x + 841 \]\begin{enumerate}[label=\Alph*.]
\item \( \text{No, because there is a $y$-value that goes to 2 different $x$-values.} \)
\item \( \text{No, because the domain of the function is not $(-\infty, \infty)$.} \)
\item \( \text{No, because there is an $x$-value that goes to 2 different $y$-values.} \)
\item \( \text{Yes, the function is 1-1.} \)
\item \( \text{No, because the range of the function is not $(-\infty, \infty)$.} \)

\end{enumerate} }
\end{enumerate}

\end{document}