\documentclass[14pt]{extbook}
\usepackage{multicol, enumerate, enumitem, hyperref, color, soul, setspace, parskip, fancyhdr} %General Packages
\usepackage{amssymb, amsthm, amsmath, bbm, latexsym, units, mathtools} %Math Packages
\everymath{\displaystyle} %All math in Display Style
% Packages with additional options
\usepackage[headsep=0.5cm,headheight=12pt, left=1 in,right= 1 in,top= 1 in,bottom= 1 in]{geometry}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{dashrule}  % Package to use the command below to create lines between items
\newcommand{\litem}[1]{\item#1\hspace*{-1cm}\rule{\textwidth}{0.4pt}}
\pagestyle{fancy}
\lhead{Progress Quiz 9}
\chead{}
\rhead{Version C}
\lfoot{8590-6105}
\cfoot{}
\rfoot{Fall 2020}
\begin{document}

\begin{enumerate}
\litem{
Subtract the following functions, then choose the domain of the resulting function from the list below.\[ f(x) = \sqrt{-5x+18}  \text{ and } g(x) = 8x^{4} +5 x^{3} +3 x^{2} +9 x + 5 \]\begin{enumerate}[label=\Alph*.]
\item \( \text{ The domain is all Real numbers except } x = a, \text{ where } a \in [0.4, 8.4] \)
\item \( \text{ The domain is all Real numbers less than or equal to } x = a, \text{ where } a \in [1.6, 4.6] \)
\item \( \text{ The domain is all Real numbers greater than or equal to } x = a, \text{ where } a \in [-7.75, 1.25] \)
\item \( \text{ The domain is all Real numbers except } x = a \text{ and } x = b, \text{ where } a \in [-8.4, -2.4] \text{ and } b \in [1.83, 8.83] \)
\item \( \text{ The domain is all Real numbers. } \)

\end{enumerate} }
\litem{
Find the inverse of the function below (if it exists). Then, evaluate the inverse at $x = -10$ and choose the interval the $f^{-1}(-10)$ belongs to.\[ f(x) = \sqrt[3]{2 x + 4} \]\begin{enumerate}[label=\Alph*.]
\item \( f^{-1}(-10) \in [501.5, 506.2] \)
\item \( f^{-1}(-10) \in [496.7, 498.8] \)
\item \( f^{-1}(-10) \in [-503, -499.6] \)
\item \( f^{-1}(-10) \in [-500.5, -497.4] \)
\item \( \text{ The function is not invertible for all Real numbers. } \)

\end{enumerate} }
\litem{
Determine whether the function below is 1-1.\[ f(x) = -18 x^2 + 93 x + 870 \]\begin{enumerate}[label=\Alph*.]
\item \( \text{No, because the domain of the function is not $(-\infty, \infty)$.} \)
\item \( \text{No, because there is an $x$-value that goes to 2 different $y$-values.} \)
\item \( \text{No, because there is a $y$-value that goes to 2 different $x$-values.} \)
\item \( \text{Yes, the function is 1-1.} \)
\item \( \text{No, because the range of the function is not $(-\infty, \infty)$.} \)

\end{enumerate} }
\litem{
Find the inverse of the function below (if it exists). Then, evaluate the inverse at $x = 10$ and choose the interval the $f^{-1}(10)$ belongs to.\[ f(x) = \sqrt[3]{2 x + 4} \]\begin{enumerate}[label=\Alph*.]
\item \( f^{-1}(10) \in [501.1, 505.8] \)
\item \( f^{-1}(10) \in [-504.2, -498.6] \)
\item \( f^{-1}(10) \in [-498.9, -495.7] \)
\item \( f^{-1}(10) \in [495.5, 500.2] \)
\item \( \text{ The function is not invertible for all Real numbers. } \)

\end{enumerate} }
\litem{
Find the inverse of the function below. Then, evaluate the inverse at $x = 9$ and choose the interval that $f^{-1}(9)$ belongs to.\[ f(x) = \ln{(x-4)}+5 \]\begin{enumerate}[label=\Alph*.]
\item \( f^{-1}(9) \in [442412.39, 442427.39] \)
\item \( f^{-1}(9) \in [56.6, 60.6] \)
\item \( f^{-1}(9) \in [45.6, 55.6] \)
\item \( f^{-1}(9) \in [152.41, 155.41] \)
\item \( f^{-1}(9) \in [1202605.28, 1202611.28] \)

\end{enumerate} }
\litem{
Choose the interval below that $f$ composed with $g$ at $x=-1$ is in.\[ f(x) = 2x^{3} -1 x^{2} -4 x + 4 \text{ and } g(x) = -x^{3} +4 x^{2} +3 x -3 \]\begin{enumerate}[label=\Alph*.]
\item \( (f \circ g)(-1) \in [-15, -9] \)
\item \( (f \circ g)(-1) \in [3, 9] \)
\item \( (f \circ g)(-1) \in [14, 15] \)
\item \( (f \circ g)(-1) \in [-21, -15] \)
\item \( \text{It is not possible to compose the two functions.} \)

\end{enumerate} }
\litem{
Choose the interval below that $f$ composed with $g$ at $x=-1$ is in.\[ f(x) = -x^{3} +2 x^{2} +x \text{ and } g(x) = 2x^{3} +3 x^{2} -x + 3 \]\begin{enumerate}[label=\Alph*.]
\item \( (f \circ g)(-1) \in [19, 27] \)
\item \( (f \circ g)(-1) \in [-73, -65] \)
\item \( (f \circ g)(-1) \in [28, 32] \)
\item \( (f \circ g)(-1) \in [-66, -56] \)
\item \( \text{It is not possible to compose the two functions.} \)

\end{enumerate} }
\litem{
Find the inverse of the function below. Then, evaluate the inverse at $x = 7$ and choose the interval that $f^{-1}(7)$ belongs to.\[ f(x) = e^{x-2}-5 \]\begin{enumerate}[label=\Alph*.]
\item \( f^{-1}(7) \in [4.31, 4.6] \)
\item \( f^{-1}(7) \in [-3.01, -2.63] \)
\item \( f^{-1}(7) \in [-3.43, -3.34] \)
\item \( f^{-1}(7) \in [0.43, 0.88] \)
\item \( f^{-1}(7) \in [-4.6, -4.26] \)

\end{enumerate} }
\litem{
Multiply the following functions, then choose the domain of the resulting function from the list below.\[ f(x) = \sqrt{-5x-27}  \text{ and } g(x) = 2x^{2} \]\begin{enumerate}[label=\Alph*.]
\item \( \text{ The domain is all Real numbers less than or equal to } x = a, \text{ where } a \in [-10.4, 0.6] \)
\item \( \text{ The domain is all Real numbers except } x = a, \text{ where } a \in [-10.25, -5.25] \)
\item \( \text{ The domain is all Real numbers greater than or equal to } x = a, \text{ where } a \in [-9, -2] \)
\item \( \text{ The domain is all Real numbers except } x = a \text{ and } x = b, \text{ where } a \in [-8.8, -4.8] \text{ and } b \in [-3.8, 0.2] \)
\item \( \text{ The domain is all Real numbers. } \)

\end{enumerate} }
\litem{
Determine whether the function below is 1-1.\[ f(x) = -24 x^2 - 176 x - 306 \]\begin{enumerate}[label=\Alph*.]
\item \( \text{No, because the domain of the function is not $(-\infty, \infty)$.} \)
\item \( \text{Yes, the function is 1-1.} \)
\item \( \text{No, because there is a $y$-value that goes to 2 different $x$-values.} \)
\item \( \text{No, because the range of the function is not $(-\infty, \infty)$.} \)
\item \( \text{No, because there is an $x$-value that goes to 2 different $y$-values.} \)

\end{enumerate} }
\end{enumerate}

\end{document}