\documentclass[14pt]{extbook}
\usepackage{multicol, enumerate, enumitem, hyperref, color, soul, setspace, parskip, fancyhdr} %General Packages
\usepackage{amssymb, amsthm, amsmath, latexsym, units, mathtools} %Math Packages
\everymath{\displaystyle} %All math in Display Style
% Packages with additional options
\usepackage[headsep=0.5cm,headheight=12pt, left=1 in,right= 1 in,top= 1 in,bottom= 1 in]{geometry}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{dashrule}  % Package to use the command below to create lines between items
\newcommand{\litem}[1]{\item#1\hspace*{-1cm}\rule{\textwidth}{0.4pt}}
\pagestyle{fancy}
\lhead{Progress Quiz 8}
\chead{}
\rhead{Version C}
\lfoot{5493-4176}
\cfoot{}
\rfoot{Summer C 2021}
\begin{document}

\begin{enumerate}
\litem{
Find the inverse of the function below (if it exists). Then, evaluate the inverse at $x = -15$ and choose the interval that $f^-1(-15)$ belongs to.\[ f(x) = 5 x^2 + 4 \]\begin{enumerate}[label=\Alph*.]
\item \( f^{-1}(-15) \in [2.55, 3.24] \)
\item \( f^{-1}(-15) \in [0.22, 1.57] \)
\item \( f^{-1}(-15) \in [5.71, 6.76] \)
\item \( f^{-1}(-15) \in [1.92, 2.48] \)
\item \( \text{ The function is not invertible for all Real numbers. } \)

\end{enumerate} }
\litem{
Find the inverse of the function below. Then, evaluate the inverse at $x = 9$ and choose the interval that $f^-1(9)$ belongs to.\[ f(x) = e^{x-5}-2 \]\begin{enumerate}[label=\Alph*.]
\item \( f^{-1}(9) \in [-0.52, 0.09] \)
\item \( f^{-1}(9) \in [6.77, 7.99] \)
\item \( f^{-1}(9) \in [-0.67, -0.3] \)
\item \( f^{-1}(9) \in [-2.85, -2.48] \)
\item \( f^{-1}(9) \in [0.5, 1.03] \)

\end{enumerate} }
\litem{
Find the inverse of the function below. Then, evaluate the inverse at $x = 8$ and choose the interval that $f^-1(8)$ belongs to.\[ f(x) = e^{x-2}-3 \]\begin{enumerate}[label=\Alph*.]
\item \( f^{-1}(8) \in [3.79, 5.33] \)
\item \( f^{-1}(8) \in [0.3, 0.72] \)
\item \( f^{-1}(8) \in [-1.81, -1.38] \)
\item \( f^{-1}(8) \in [-0.85, -0.59] \)
\item \( f^{-1}(8) \in [-1.27, -1.04] \)

\end{enumerate} }
\litem{
Multiply the following functions, then choose the domain of the resulting function from the list below.\[ f(x) = \frac{4}{6x+29} \text{ and } g(x) = \frac{4}{4x-17} \]\begin{enumerate}[label=\Alph*.]
\item \( \text{ The domain is all Real numbers less than or equal to } x = a, \text{ where } a \in [-8.33, 4.67] \)
\item \( \text{ The domain is all Real numbers greater than or equal to } x = a, \text{ where } a \in [-4.25, -2.25] \)
\item \( \text{ The domain is all Real numbers except } x = a, \text{ where } a \in [-9.17, -1.17] \)
\item \( \text{ The domain is all Real numbers except } x = a \text{ and } x = b, \text{ where } a \in [-8.83, -2.83] \text{ and } b \in [4.25, 8.25] \)
\item \( \text{ The domain is all Real numbers. } \)

\end{enumerate} }
\litem{
Determine whether the function below is 1-1.\[ f(x) = -36 x^2 - 342 x - 756 \]\begin{enumerate}[label=\Alph*.]
\item \( \text{No, because the domain of the function is not $(-\infty, \infty)$.} \)
\item \( \text{No, because there is a $y$-value that goes to 2 different $x$-values.} \)
\item \( \text{Yes, the function is 1-1.} \)
\item \( \text{No, because there is an $x$-value that goes to 2 different $y$-values.} \)
\item \( \text{No, because the range of the function is not $(-\infty, \infty)$.} \)

\end{enumerate} }
\litem{
Choose the interval below that $f$ composed with $g$ at $x=-1$ is in.\[ f(x) = -x^{3} +2 x^{2} +2 x -2 \text{ and } g(x) = -4x^{3} -2 x^{2} +x \]\begin{enumerate}[label=\Alph*.]
\item \( (f \circ g)(-1) \in [-3, 5] \)
\item \( (f \circ g)(-1) \in [-3, 5] \)
\item \( (f \circ g)(-1) \in [-6, -1] \)
\item \( (f \circ g)(-1) \in [-8, -5] \)
\item \( \text{It is not possible to compose the two functions.} \)

\end{enumerate} }
\litem{
Find the inverse of the function below (if it exists). Then, evaluate the inverse at $x = 14$ and choose the interval that $f^-1(14)$ belongs to.\[ f(x) = 5 x^2 + 3 \]\begin{enumerate}[label=\Alph*.]
\item \( f^{-1}(14) \in [5.96, 6.85] \)
\item \( f^{-1}(14) \in [3.46, 3.64] \)
\item \( f^{-1}(14) \in [1.66, 2.16] \)
\item \( f^{-1}(14) \in [1.43, 1.51] \)
\item \( \text{ The function is not invertible for all Real numbers. } \)

\end{enumerate} }
\litem{
Choose the interval below that $f$ composed with $g$ at $x=-1$ is in.\[ f(x) = 4x^{3} + x^{2} -x -1 \text{ and } g(x) = -x^{3} -1 x^{2} +x \]\begin{enumerate}[label=\Alph*.]
\item \( (f \circ g)(-1) \in [21, 24] \)
\item \( (f \circ g)(-1) \in [-9, 1] \)
\item \( (f \circ g)(-1) \in [11, 16] \)
\item \( (f \circ g)(-1) \in [3, 7] \)
\item \( \text{It is not possible to compose the two functions.} \)

\end{enumerate} }
\litem{
Subtract the following functions, then choose the domain of the resulting function from the list below.\[ f(x) = \sqrt{-6x-23}  \text{ and } g(x) = 7x^{2} +4 x + 8 \]\begin{enumerate}[label=\Alph*.]
\item \( \text{ The domain is all Real numbers greater than or equal to } x = a, \text{ where } a \in [-10, -5] \)
\item \( \text{ The domain is all Real numbers except } x = a, \text{ where } a \in [-6.67, -3.67] \)
\item \( \text{ The domain is all Real numbers less than or equal to } x = a, \text{ where } a \in [-8.83, 4.17] \)
\item \( \text{ The domain is all Real numbers except } x = a \text{ and } x = b, \text{ where } a \in [-0.75, 9.25] \text{ and } b \in [4.25, 6.25] \)
\item \( \text{ The domain is all Real numbers. } \)

\end{enumerate} }
\litem{
Determine whether the function below is 1-1.\[ f(x) = -12 x^2 - 57 x - 63 \]\begin{enumerate}[label=\Alph*.]
\item \( \text{Yes, the function is 1-1.} \)
\item \( \text{No, because there is an $x$-value that goes to 2 different $y$-values.} \)
\item \( \text{No, because there is a $y$-value that goes to 2 different $x$-values.} \)
\item \( \text{No, because the range of the function is not $(-\infty, \infty)$.} \)
\item \( \text{No, because the domain of the function is not $(-\infty, \infty)$.} \)

\end{enumerate} }
\end{enumerate}

\end{document}