\documentclass[14pt]{extbook}
\usepackage{multicol, enumerate, enumitem, hyperref, color, soul, setspace, parskip, fancyhdr} %General Packages
\usepackage{amssymb, amsthm, amsmath, latexsym, units, mathtools} %Math Packages
\everymath{\displaystyle} %All math in Display Style
% Packages with additional options
\usepackage[headsep=0.5cm,headheight=12pt, left=1 in,right= 1 in,top= 1 in,bottom= 1 in]{geometry}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{dashrule}  % Package to use the command below to create lines between items
\newcommand{\litem}[1]{\item#1\hspace*{-1cm}\rule{\textwidth}{0.4pt}}
\pagestyle{fancy}
\lhead{Progress Quiz 8}
\chead{}
\rhead{Version A}
\lfoot{5493-4176}
\cfoot{}
\rfoot{Summer C 2021}
\begin{document}

\begin{enumerate}
\litem{
Find the inverse of the function below (if it exists). Then, evaluate the inverse at $x = 15$ and choose the interval that $f^-1(15)$ belongs to.\[ f(x) = \sqrt[3]{3 x - 4} \]\begin{enumerate}[label=\Alph*.]
\item \( f^{-1}(15) \in [-1128.5, -1124.2] \)
\item \( f^{-1}(15) \in [1124.3, 1128.9] \)
\item \( f^{-1}(15) \in [-1124.2, -1120.8] \)
\item \( f^{-1}(15) \in [1121.9, 1125.8] \)
\item \( \text{ The function is not invertible for all Real numbers. } \)

\end{enumerate} }
\litem{
Find the inverse of the function below. Then, evaluate the inverse at $x = 7$ and choose the interval that $f^-1(7)$ belongs to.\[ f(x) = e^{x+5}-3 \]\begin{enumerate}[label=\Alph*.]
\item \( f^{-1}(7) \in [-2.55, -2.18] \)
\item \( f^{-1}(7) \in [-1.84, -0.93] \)
\item \( f^{-1}(7) \in [-3.14, -2.59] \)
\item \( f^{-1}(7) \in [6.87, 7.36] \)
\item \( f^{-1}(7) \in [-0.62, -0.27] \)

\end{enumerate} }
\litem{
Find the inverse of the function below. Then, evaluate the inverse at $x = 7$ and choose the interval that $f^-1(7)$ belongs to.\[ f(x) = e^{x-5}+3 \]\begin{enumerate}[label=\Alph*.]
\item \( f^{-1}(7) \in [5.43, 5.54] \)
\item \( f^{-1}(7) \in [5.12, 5.31] \)
\item \( f^{-1}(7) \in [6.27, 6.45] \)
\item \( f^{-1}(7) \in [3.54, 3.82] \)
\item \( f^{-1}(7) \in [-3.62, -3.52] \)

\end{enumerate} }
\litem{
Multiply the following functions, then choose the domain of the resulting function from the list below.\[ f(x) = 6x^{4} +4 x^{2} +7 x + 3 \text{ and } g(x) = \sqrt{-6x-27}  \]\begin{enumerate}[label=\Alph*.]
\item \( \text{ The domain is all Real numbers except } x = a, \text{ where } a \in [6.25, 9.25] \)
\item \( \text{ The domain is all Real numbers greater than or equal to } x = a, \text{ where } a \in [3.5, 10.5] \)
\item \( \text{ The domain is all Real numbers less than or equal to } x = a, \text{ where } a \in [-12.5, -1.5] \)
\item \( \text{ The domain is all Real numbers except } x = a \text{ and } x = b, \text{ where } a \in [1.4, 5.4] \text{ and } b \in [1.25, 7.25] \)
\item \( \text{ The domain is all Real numbers. } \)

\end{enumerate} }
\litem{
Determine whether the function below is 1-1.\[ f(x) = 18 x^2 - 42 x - 196 \]\begin{enumerate}[label=\Alph*.]
\item \( \text{No, because there is a $y$-value that goes to 2 different $x$-values.} \)
\item \( \text{No, because the range of the function is not $(-\infty, \infty)$.} \)
\item \( \text{Yes, the function is 1-1.} \)
\item \( \text{No, because the domain of the function is not $(-\infty, \infty)$.} \)
\item \( \text{No, because there is an $x$-value that goes to 2 different $y$-values.} \)

\end{enumerate} }
\litem{
Choose the interval below that $f$ composed with $g$ at $x=-1$ is in.\[ f(x) = 3x^{3} +2 x^{2} -4 x -4 \text{ and } g(x) = 3x^{3} + x^{2} +2 x + 3 \]\begin{enumerate}[label=\Alph*.]
\item \( (f \circ g)(-1) \in [1.9, 4.3] \)
\item \( (f \circ g)(-1) \in [-2.4, 0.1] \)
\item \( (f \circ g)(-1) \in [-2.4, 0.1] \)
\item \( (f \circ g)(-1) \in [5.6, 7.5] \)
\item \( \text{It is not possible to compose the two functions.} \)

\end{enumerate} }
\litem{
Find the inverse of the function below (if it exists). Then, evaluate the inverse at $x = 12$ and choose the interval that $f^-1(12)$ belongs to.\[ f(x) = \sqrt[3]{5 x + 2} \]\begin{enumerate}[label=\Alph*.]
\item \( f^{-1}(12) \in [-345.36, -344.52] \)
\item \( f^{-1}(12) \in [345.63, 346.11] \)
\item \( f^{-1}(12) \in [-346.21, -345.48] \)
\item \( f^{-1}(12) \in [344.56, 345.27] \)
\item \( \text{ The function is not invertible for all Real numbers. } \)

\end{enumerate} }
\litem{
Choose the interval below that $f$ composed with $g$ at $x=-1$ is in.\[ f(x) = x^{3} -1 x^{2} -2 x \text{ and } g(x) = -3x^{3} +3 x^{2} -x -2 \]\begin{enumerate}[label=\Alph*.]
\item \( (f \circ g)(-1) \in [89, 92] \)
\item \( (f \circ g)(-1) \in [-13, -8] \)
\item \( (f \circ g)(-1) \in [81, 89] \)
\item \( (f \circ g)(-1) \in [-2, 0] \)
\item \( \text{It is not possible to compose the two functions.} \)

\end{enumerate} }
\litem{
Subtract the following functions, then choose the domain of the resulting function from the list below.\[ f(x) = \frac{3}{4x-23} \text{ and } g(x) = \frac{2}{4x-29} \]\begin{enumerate}[label=\Alph*.]
\item \( \text{ The domain is all Real numbers except } x = a, \text{ where } a \in [6.67, 12.67] \)
\item \( \text{ The domain is all Real numbers greater than or equal to } x = a, \text{ where } a \in [-12, 1] \)
\item \( \text{ The domain is all Real numbers less than or equal to } x = a, \text{ where } a \in [0.4, 5.4] \)
\item \( \text{ The domain is all Real numbers except } x = a \text{ and } x = b, \text{ where } a \in [-2.25, 7.75] \text{ and } b \in [6.25, 10.25] \)
\item \( \text{ The domain is all Real numbers. } \)

\end{enumerate} }
\litem{
Determine whether the function below is 1-1.\[ f(x) = 18 x^2 + 15 x - 375 \]\begin{enumerate}[label=\Alph*.]
\item \( \text{No, because the domain of the function is not $(-\infty, \infty)$.} \)
\item \( \text{No, because there is an $x$-value that goes to 2 different $y$-values.} \)
\item \( \text{No, because there is a $y$-value that goes to 2 different $x$-values.} \)
\item \( \text{Yes, the function is 1-1.} \)
\item \( \text{No, because the range of the function is not $(-\infty, \infty)$.} \)

\end{enumerate} }
\end{enumerate}

\end{document}