\documentclass{extbook}[14pt]
\usepackage{multicol, enumerate, enumitem, hyperref, color, soul, setspace, parskip, fancyhdr, amssymb, amsthm, amsmath, bbm, latexsym, units, mathtools}
\everymath{\displaystyle}
\usepackage[headsep=0.5cm,headheight=0cm, left=1 in,right= 1 in,top= 1 in,bottom= 1 in]{geometry}
\usepackage{dashrule}  % Package to use the command below to create lines between items
\newcommand{\litem}[1]{\item#1\hspace*{-1cm}\rule{\textwidth}{0.4pt}}
\pagestyle{fancy}
\lhead{}
\chead{Answer Key for Progress Quiz 1 Version C}
\rhead{}
\lfoot{3882-3329}
\cfoot{}
\rfoot{Fall 2020}
\begin{document}
\textbf{This key should allow you to understand why you choose the option you did (beyond just getting a question right or wrong). \href{https://xronos.clas.ufl.edu/mac1105spring2020/courseDescriptionAndMisc/Exams/LearningFromResults}{More instructions on how to use this key can be found here}.}

\textbf{If you have a suggestion to make the keys better, \href{https://forms.gle/CZkbZmPbC9XALEE88}{please fill out the short survey here}.}

\textit{Note: This key is auto-generated and may contain issues and/or errors. The keys are reviewed after each exam to ensure grading is done accurately. If there are issues (like duplicate options), they are noted in the offline gradebook. The keys are a work-in-progress to give students as many resources to improve as possible.}

\rule{\textwidth}{0.4pt}

\begin{enumerate}\litem{



\textbf{General Comment:} None
}
\litem{
Simplify the expression below into the form $a+bi$. Then, choose the intervals that $a$ and $b$ belong to.
\[ \frac{-27 - 77 i}{-2 - 4 i} \]
The solution is \( [18.1, 2.3] \), which is option B.\begin{enumerate}[label=\Alph*.]
\item \( a \in [-13.5, -12] \text{ and } b \in [12.5, 13.5] \) $-12.70  + 13.10 i$, which corresponds to forgetting to multiply the conjugate by the numerator and not computing the conjugate correctly.
\item \( a \in [17, 19] \text{ and } b \in [1.5, 2.5] \)* $18.10  + 2.30 i$, which is the correct option.
\item \( a \in [17, 19] \text{ and } b \in [45.5, 46.5] \) $18.10  + 46.00 i$, which corresponds to forgetting to multiply the conjugate by the numerator.
\item \( a \in [361, 362.5] \text{ and } b \in [1.5, 2.5] \) $362.00  + 2.30 i$, which corresponds to forgetting to multiply the conjugate by the numerator and using a plus instead of a minus in the denominator.
\item \( a \in [12, 14] \text{ and } b \in [18.5, 20] \) $13.50  + 19.25 i$, which corresponds to just dividing the first term by the first term and the second by the second.
\end{enumerate}

\textbf{General Comment:} Multiply the numerator and denominator by the *conjugate* of the denominator, then simplify. For example, if we have $2+3i$, the conjugate is $2-3i$.
}
\litem{
Simplify the expression below into the form $a+bi$. Then, choose the intervals that $a$ and $b$ belong to.
\[ (-5 + 7 i)(4 - 6 i) \]
The solution is \( 22 + 58 i \), which is option D.\begin{enumerate}[label=\Alph*.]
\item \( a \in [-63, -61] \text{ and } b \in [-3, -1] \) $-62 - 2 i$, which corresponds to adding a minus sign in the second term.
\item \( a \in [-24, -17] \text{ and } b \in [-46, -37] \) $-20 - 42 i$, which corresponds to just multiplying the real terms to get the real part of the solution and the coefficients in the complex terms to get the complex part.
\item \( a \in [-63, -61] \text{ and } b \in [2, 4] \) $-62 + 2 i$, which corresponds to adding a minus sign in the first term.
\item \( a \in [17, 24] \text{ and } b \in [55, 59] \)* $22 + 58 i$, which is the correct option.
\item \( a \in [17, 24] \text{ and } b \in [-61, -57] \) $22 - 58 i$, which corresponds to adding a minus sign in both terms.
\end{enumerate}

\textbf{General Comment:} You can treat $i$ as a variable and distribute. Just remember that $i^2=-1$, so you can continue to reduce after you distribute.
}
\end{enumerate}

\end{document}