\documentclass{extbook}[14pt]
\usepackage{multicol, enumerate, enumitem, hyperref, color, soul, setspace, parskip, fancyhdr, amssymb, amsthm, amsmath, bbm, latexsym, units, mathtools}
\everymath{\displaystyle}
\usepackage[headsep=0.5cm,headheight=0cm, left=1 in,right= 1 in,top= 1 in,bottom= 1 in]{geometry}
\usepackage{dashrule}  % Package to use the command below to create lines between items
\newcommand{\litem}[1]{\item #1

\rule{\textwidth}{0.4pt}}
\pagestyle{fancy}
\lhead{}
\chead{Answer Key for test Version A}
\rhead{}
\lfoot{1466-9383}
\cfoot{}
\rfoot{testing}
\begin{document}
\textbf{This key should allow you to understand why you choose the option you did (beyond just getting a question right or wrong). \href{https://xronos.clas.ufl.edu/mac1105spring2020/courseDescriptionAndMisc/Exams/LearningFromResults}{More instructions on how to use this key can be found here}.}

\textbf{If you have a suggestion to make the keys better, \href{https://forms.gle/CZkbZmPbC9XALEE88}{please fill out the short survey here}.}

\textit{Note: This key is auto-generated and may contain issues and/or errors. The keys are reviewed after each exam to ensure grading is done accurately. If there are issues (like duplicate options), they are noted in the offline gradebook. The keys are a work-in-progress to give students as many resources to improve as possible.}

\rule{\textwidth}{0.4pt}

\begin{enumerate}\litem{
First, find the equation of the line containing the two points below. Then, write the equation as $ y=mx+b $ and choose the intervals that contain $m$ and $b$.
\[ (-5, -10) \text{ and } (-8, 5) \]

The solution is \( y = -5.0x -35.0 \), which is option E.\begin{enumerate}[label=\Alph*.]
\item \( m \in [-8, -4] \hspace*{3mm} b \in [32, 37] \)

 $y = -5.0x + 35.0$, which corresponds to using the correct slope and getting the negative y-intercept.
\item \( m \in [-8, -4] \hspace*{3mm} b \in [7, 20] \)

 $y = -5.0x + 13$, which corresponds to using the correct slope/equation but not distributing correctly using the second point.
\item \( m \in [-8, -4] \hspace*{3mm} b \in [-6, -3] \)

 $y = -5.0x -5$, which corresponds to using the correct slope/equation but not distributing correctly using the first point.
\item \( m \in [2, 7] \hspace*{3mm} b \in [42, 46] \)

 $y = 5.0x + 45.0$, which corresponds to using the negative slope and the correct equation.
\item \( m \in [-8, -4] \hspace*{3mm} b \in [-35, -29] \)

* $y = -5.0x -35.0$, which is the correct option.
\end{enumerate}

\textbf{General Comment:} Remember to keep your points in order when plugging in to the slope formula.
}
\end{enumerate}

\end{document}